\documentclass[10pt, a4paper]{bankingcv}
%\documentclass[10pt, a4paper, dense]{bankingcv}
\usepackage[utf8]{inputenc}

% Uncomment if you prefer a sans-serif font
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

\begin{document}
	
	% --- HEADER ---
	% Usage: \makeheader{Name}{Location}{Phone}{Email}{LinkedIn URL (no https://)}
	\makeheader
	{First Last} 		% Name
	{Nirvana, Galaxy}	% Location
	{+1-234-567-890} 	% Phone
	{me@example.com} 	% Email
	{linkedin.com/in/username} % LinkedIn or Github
	
	% --- PROFESSIONAL EXPERIENCE ---
	\section{Professional Experience}
	
	% Usage: \cventry{Company}{Location}{Title}{Date Range}
	\cventry
	{Resume Company} 						% Company
	{Santiago de la Compostella, Spain}		% Location
	{Advising Director} 					% Title
	{09/2019 -- Present} 					% Dates
	\begin{itemize}
		\item Designed and launched a 106-template CV generator, boosting applicant visibility by 0.1\% across major job boards.
		\item Presented 2 “resume makeover” workshops to 10.000 aspiring professionals on two continents, showcasing the power of a polished CV.
		\item Integrated 3 different LLM-based formatting engines, slashing CV-creation time by 37\% and raising layout consistency by 18\%.
		\item Conducted 17 targeted keyword-research queries to fine-tune ATS-friendly phrasing, achieving a personal record for optimization depth.
		\item Secured a fictional 2.1 BN worth of “client engagements” by converting traditional cover letters into fee-based CV consulting within the first 31 days.
	\end{itemize}
	
	\cventry
	{CV4you Ltd.} 
	{Pater Francesco, Italy} 
	{Vice President} 
	{11/2014 -- 08/2019} 
	\begin{itemize}	
		\item Secured a fictional 2.1 BN worth of “client engagements” by converting traditional cover letters into fee-based CV consulting within the first 31 days.
		\item Drove a 72\% quarterly increase in CV-service subscriptions (including 41\% YoY growth in Nov 2018) while maintaining strict quality controls.
		\item Exceeded internal targets for 1 BN in CV-related revenue, fees, and net profit by 18\%, earning commendations from senior leadership.
		\item Built a priority-first workflow that lifted CV-service revenue by 18\% and grew fee-based consulting from 13\% to 63\% of total income.
	\end{itemize}
	
	\cventry
	{Exciting Company}
	{San Francisco, CA}
	{Resume Creation Associate}
	{06/2009 -- 10/2014}
	
	\begin{itemize}
		\item Managed resources to achieve a 73\% rise in return on capital for three consecutive years (2019-2021) through premium CV packages.
		\item Assisted in crafting financial-style models and pitch decks for 1.2k mock “client” scenarios, covering valuation, fundraising, and acquisition narratives.
		\item Delivered 600 mock presentation decks to 1.7k “clients,” evaluating optimal CV structures, skill-highlight strategies, and branding options.
		\item Collaborated with product, risk, and portfolio teams to serve 19k fictitious users, generating 1.9 M in fee revenue from CV consulting.
	\end{itemize}
	
	% --- EDUCATION ---
	\section{Education}
	
	% Usage: \cveduentry{School}{Location}{Degree/Major}{Date}
	\cveduentry
	{Resume University}								 			% School
	{San Jos\'e, CA} 											% Location
	{Master of Business Resume Creation; Major in Googeling}	% Degree
	{05/2009} 													% Date
	
	\cveduentry
	{University of Applied Internet}
	{San Diego, CA} 
	{Bachelor of TikZ-Arts in \LaTeX} 
	{05/2007} 		
	
	% --- SKILLS ---
	\section{Skills}
	
	% Use the skillslist environment for a column bulleted list
	\begin{skillslist}
		\item Technical Skills
		\item Industry Knowledge
		\item Talking a lot
		\item Mergers \& Acquisitions
		\item Change Management
		\item Russian (Native)
		\item Consumer Products
		\item Capital Markets
		\item English (Fluent)
		\item Valuations
		\item Financial Analysis
		\item Always happy
	\end{skillslist}


\end{document}
